Exploring Disparate Data: Part 1

### 2024-11-03 A3-Pt1.Rmd
cyclones_data_update_0 All tests passed!
Update A3-Pt1.Rmd

-   Aditya
-   Andy
-   Dibu
-   Oscar
-   Taras

@@

```{r error=TRUE}
# YOUR CODE HERE

print(cyclones_data_update_0)
```

@@

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE

>>>>

-   Aditya (169027493)
-   Andy
-   Dibu
-   Oscar
-   Taras

@@

```{r error=TRUE}
# YOUR CODE HERE
cyclones_data_update_0 <- bind_rows(at_cyclone, np_cyclone)
print(cyclones_data_update_0)
```

@@

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE
    group_by(year, region) |>
    summarize(
        min = min(ice_extent, na.rm = TRUE),
        max = max(ice_extent, na.rm = TRUE)
    ) |>
    pivot_longer(
        cols = c("min", "max"),
        names_to = "name",
        values_to = "value"
    )
